---
title: "Untitled"
author: "roywei"
Date: " `r Sys.Date()` "

output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 调用要使用的R包
```{r load R package,message= F}
require(pedquant)
require(tidytable)
require(purrr)
require(ggplot2)
```

#获取数据整理数据
```{r get index data,echo=F}
etf<- c('510050.SS','510300.SS','159919.SZ','000300.SS','000852.SS','510500.SS','159915.SZ','159922.SZ','159901.SZ','000016.SS')
pedquant::md_stock(etf,date_range = '3y') %>% 
    purrr::map(~select.(.,date,close)) %>% 
    purrr::map(~quantmod::dailyReturn(.,type = 'log')) %>% 
  reduce(merge) %>% 
  `colnames<-`(etf) ->ret1
ret1 %>% head() %>% 
  pander::pander(split.table=Inf)
```
数据整理宽数据变长数据，并绘制图
## 数据描述统计
```{r}
ret1 %>% 
  psych::describe()
ret1 %>% 
  summarytools::descr()
ret1 %>% 
  summarytools::dfSummary()
ret1 %>% 
  skimr::skim()
ret1 %>% 
  pastecs::stat.desc(norm = T)
```


## 数据变化及展示
### 宽变长
```{r}
ret1 %>%timetk::tk_tbl(rename_index = 'Date') %>% 
    tidytable::pivot_longer(cols = -Date,names_to = 'stock',values_to = 'return')->ret_long
ggplot2::ggplot(ret_long,mapping = aes(x=Date,y=return,color=stock))+geom_path(stat = "identity") +
    facet_grid(stock ~ .) + theme_minimal() + labs(x = "Date", y = "returns")
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
