---
title: "Untitled"
author: "roywei"
Date: " `r Sys.Date()` "

output: github_document
---

```{r setup, tidy='styler',include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
# 调用要使用的R包
```{r load R package,message= F}
require(pedquant)
require(tidytable)
require(purrr)
require(ggplot2)
```

#获取数据整理数据
```{r get index data,echo=F}
etf<- c('510050.SS','510300.SS','159919.SZ','000300.SS','000852.SS','510500.SS','159915.SZ','159922.SZ','159901.SZ','000016.SS')
pedquant::md_stock(etf,date_range = '3y') %>% 
    purrr::map(~select.(.,date,close)) %>% 
    purrr::map(~quantmod::dailyReturn(.,type = 'log')) %>% 
  reduce(merge) %>% 
  `colnames<-`(etf) ->ret1
ret1 %>% head() %>% 
  pander::pander(split.table=Inf)
```
数据整理宽数据变长数据，并绘制图
## 数据描述统计
```{r}
ret1 %>% 
  psych::describe()
ret1 %>% 
  summarytools::descr()
ret1 %>% 
  summarytools::dfSummary()
ret1 %>% 
  skimr::skim()
ret1 %>% 
  pastecs::stat.desc(norm = T)
```


## 数据变化及展示
### 宽变长
```{r}
ret1 %>%timetk::tk_tbl(rename_index = 'Date') %>% 
    tidytable::pivot_longer(cols = -Date,names_to = 'stock',values_to = 'return')->ret_long
ggplot2::ggplot(ret_long,mapping = aes(x=Date,y=return,color=stock))+geom_path(stat = "identity") +
    facet_grid(stock ~ .) + theme_minimal() + labs(x = "Date", y = "returns")
```

## GitHub Documents

This is an R Markdown format used for publishing markdown documents to GitHub. When you click the **Knit** button all R code chunks are run and a markdown file (.md) suitable for publishing to GitHub is generated.

## Including Code

You can include R code in the document as follows:

```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.

数据清理，生成变量以便于机器学习使用
```{r ml,tidy='styler'}
require(tidytable)
require(tidyquant)
require(pedquant)
test <- md_stock('510500.ss',date_range = '10y') %>% bind_rows()

test %>%
tq_mutate(select = close_adj,
mutate_fun =  SMA,
n=5,
col_rename = 'sma5') %>%
tq_mutate(select = close_adj,
mutate_fun =  EMA,
n=5,
col_rename = 'ema5') %>%
tq_mutate(select = close_adj,
mutate_fun =  RSI,
n=5,
col_rename = "rsi") %>%
tq_mutate(select = close_adj,
mutate_fun =  dailyReturn,
type = 'log',
col_rename = 'ret1') ->test1
test %>%
tq_mutate(select = close_adj,
mutate_fun =  SMA,
n=5,
col_rename = 'sma5') %>%
tq_mutate(select = close_adj,
mutate_fun =  EMA,
n=5,
col_rename = 'ema5') %>%
tq_mutate(select = close_adj,
mutate_fun =  RSI,
n=5,
col_rename = 'rsi') %>%
tq_mutate(select = close_adj,
mutate_fun =  dailyReturn,
type = 'log',
col_rename = 'ret1') ->test1

test1 %>%
tq_mutate(select = close_adj,
mutate_fun = MACD,
) %>%
mutate(Direction = ifelse(close_adj >= lag(close_adj, 5), 1, 0)) %>%
select(9:ncol(.)) %>%
mutate(sma5=lag(sma5),ema5=lag(ema5),rsi=lag(rsi),ret1=lag(ret1),sigal=lag(signal),macd=lag(macd)) %>% select(Direction,ret1,sma5,ema5,macd,signal,rsi) %>%
drop_na() %>%
`colnames<-`(c("Direction", "Ret", "SMA", "EMA", "MACD", "Signal",
"RSI"))->d_ex1

#使用逻辑斯蒂回归进行分类预测 
# remove NAs
d_ex1 = na.omit(d_ex1)
# convert to data frame
d_ex1 = as.data.frame(d_ex1)
# convert direction to a factor for classification

d_ex1$Direction = as.factor(d_ex1$Direction)

idx1 = c(1:round(nrow(d_ex1) * 0.7))  #create index for first 70% values to be in the testing set
d_train1 = d_ex1[idx1, ]  #training set
d_test1 = d_ex1[-idx1, ]  #testing set
library(caret)
set.seed(999)
# control
cntrl1 = trainControl(method = "timeslice", initialWindow = 250, horizon = 30,
    fixedWindow = TRUE)
# preprocesing
prep1 = c("center", "scale")
# logistic regression
logit_ex1 = train(Direction ~ ., data = d_train1, method = "glm", family = "binomial",
    trControl = cntrl1, preProcess = prep1)
logit_ex1  #final model accuracy
summary(logit_ex1$finalModel)  #summary of the final model
# 预测变量重要图示
library(vip)
vip(logit_ex1, geom = "point") + theme_minimal()
# 使用混淆矩阵分析预测精度
pred1 = predict(logit_ex1, newdata = d_test1)  #prediction on the test data
confusionMatrix(data = pred1, reference = d_test1$Direction)
```

